---
title: "Final_Project_DSC520_Shauna_Smith"
author: "Shauna Smith"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

You are now on to the final phase of your research paper.  While this step does not require you build a model, you are welcome to do so if you feel you have the time. Instead, you need to make a recommendation for the approach you would take and what the remaining steps would be using the information you have learned in this course to take this project from simply being an analysis exercise to proposed implementation of a solution.
Overall, write a coherent narrative that tells a story with the data as you complete this section.
Summarize the problem statement you addressed. 
Summarize how you addressed this problem statement (the data used and the methodology employed, including a recommendation for a model that could be implemented). 
Summarize the interesting insights that your analysis provided. 
Summarize the implications to the consumer (target audience) of your analysis. 
Discuss the limitations of your analysis and how you, or someone else, could improve or build on it.
You can use the following template for Step 3:
A story / narrative that emerged from your data. Follow this structure.
Introduction.
The problem statement you addressed. 
How you addressed this problem statement
Analysis
Implications
Limitations
Concluding Remarks

```{r}
install.packages("Tidyverse")
library(tidyverse)
```

```{r}
setwd("/Users/Shaun/OneDrive/Documents")
VTT <- read.csv("VTT DataSet.csv")
#run a sample size test needed
power.t.test(delta = 0.2, sd=0.5, power = 0.8)
```
Here, we can test the existing data set
```{r}
t.test(Complication.Status~Visual.Training.Technique.used, data = VTT, alternative="two.sided")

```

Additional discovery process post simplifying the data set:

```{r}

SimpleVTT<-VTT%>%
  select(Complication.Status,Recovery.Duration.in.days,Visual.Training.Technique.used)

VTT_Data <- data.frame(SimpleVTT)


colnames(VTT_Data)<- c("Complication", "Duration", "Technique")
str(VTT_Data)
```

What was the analysis revealing? When the dataset was analyzed what was the conclusion derived from the results? See the following in the outputs provided

```{r}
install.packages("car")
library(car)
install.packages("mlogit")
library(mlogit)


logrvtt<-glm(Complication~Technique,data=VTT_Data,family="binomial")
summary(logrvtt)
modelchi<-logrvtt$null.deviance-logrvtt$deviance
chidf<-logrvtt$df.null-logrvtt$df.residual
chipvtt<-1-pchisq(modelchi,chidf)
chipvtt
R2vtt<-modelchi/logrvtt$null.deviance
R2vtt
testerlog<-glm(Complication~.,data=VTT_Data,family = "binomial")
summary(testerlog)


```
What are the implications and how do they effect our audience?

```{r}
install.packages("rpart")
library(rpart)
VTTree<-rpart(Complication~Technique+Duration, data=VTT_Data)
install.packages("rpart.plot")
library(rpart.plot)
rpart.plot(VTTree)

ponder<-kmeans(VTT_Data,2)



```